Road Segment Prioritization for Bicycle Infrastructure

### 2021-01-09 README.Rmd
edit section 5

# Data and Geographical Scale of Analysis

@@

Using existing cycling demand to inform decisions on where cycling infrastructure should be added reinforces existing cycling patterns and ignores potential cycling demand that could be satisfied by a connected network. To avoid this issue, @duthie2014optimization choose to ignore existing demand completely, and focus on creating a network that connects the entire study area. @olmos2020data obtain the distance distribution of cyclists using a smartphone-based bicycle GPS data, and then use a rejection-sampling algorithm on the OD data of the study area to match the potential demand distribution to the distribution obtained from GPS data.

For our purposes, we use a logistic regression model to calculate potential cycling demand. The model is adopted directly from the Propensity to Cycle Tool (PCT) [@lovelace2017propensity]. The PCT estimates  the proportion of cyclists ($\boldsymbol{C_{p}}$) for each MSOA pair should the government achieve its target of doubling cycling by 2025. The logistic regression model used to calculate $\boldsymbol{C_{p}}$ has the following parameters:

@@

The next step is to route the potential cycling demand ($\boldsymbol{C_{p}}$) between all OD pairs onto the road network. 
<!-- This expands on the work of @mauttone2017bicycle, by going beyond simply favoring roads with existing cycling infrastructure to creating a hierarchy of road preference. -->

@@

The above points are accounted for by using a weighted road network for routing. This has previously been done by multiplying all road segments without cycling infrastructure by an impedance factor [@mauttone2017bicycle], or by assigning a weight to the road segment proportional to the investment cost of bringing it to an acceptable level of stress for cycling  [@duthie2014optimization]. Our approach is similar to the latter, as we create a weighting profile that is adjusted to favor less stressful streets (based on information from Table  \@ref(table:osmroadtypes)), and roads with existing cycling infrastructure. We believe this to be more practical  than the approach adopted by @mauttone2017bicycle, as it goes beyond simply favoring roads with existing cycling infrastructure to creating a hierarchy of road preference based on perceived stress levels. The approach is also in line with the creation of LTNs, as residential streets are those where motorized traffic is most likely to be banned in the creation of LTNs.

@@

All weights are between 0 and 1, and the values in the \textit{Weighted} profile are chosen so as to be inversely proportional to the stress level experienced by cyclists on them. The \textit{Unweighted} weighting profile is used to compare increases in route length resulting from two different approaches:

>>>>

<!-- # Data and Geographical Scale of Analysis -->

@@

Relying only on existing cycling activity to prioritize cycling infrastructure can reinforce existing cycling patterns and ignores potential cycling demand that could be satisfied by a connected network. To avoid this issue, @duthie2014optimization choose to ignore existing demand completely, and focus on creating a network that connects the entire study area. @olmos2020data obtain the distance distribution of cyclists using a smartphone-based bicycle GPS data, and then use a rejection-sampling algorithm on the OD data of the study area to match the potential demand distribution to the distribution obtained from GPS data.

For our purposes, we use a logistic regression model to calculate potential cycling demand. The model was adopted from the Propensity to Cycle Tool (PCT), which estimates the proportion of trips ($\boldsymbol{C_{p}}$) for each origin-destination pair that would cycle under different scenarios of change (we used the Government Target scenario, representing a nationwide target of doubling cycling by 2025) as a function of distance and hilliness [@lovelace2017propensity]. The logistic regression model used to calculate $\boldsymbol{C_{p}}$ has the following parameters:

@@

The next step in our approach is to route the potential cycling demand ($\boldsymbol{C_{p}}$) between all OD pairs onto the road network. We choose not to use the PCT approach for routing as it is reliant on external and therefore inflexible routing services.
<!-- This expands on the work of @mauttone2017bicycle, by going beyond simply favoring roads with existing cycling infrastructure to creating a hierarchy of road preference. -->

@@

The above points are accounted for by using a weighted road network for routing. This has previously been done by multiplying all road segments without cycling infrastructure by an impedance factor [@mauttone2017bicycle], or by assigning different weights to the road segments proportional to the investment cost of bringing them to an acceptable level of stress for cycling  [@duthie2014optimization]. Our approach is similar to the latter, as we create a weighting profile that is adjusted to favor less stressful streets (based on information from Table  \@ref(table:osmroadtypes)), and roads with existing cycling infrastructure. We believe this to be more practical  than the approach adopted by @mauttone2017bicycle, as it goes beyond simply favoring roads with existing cycling infrastructure to creating a hierarchy of road preference based on perceived stress levels. The approach is also in line with the creation of LTNs, as residential streets are those where motorized traffic is most likely to be banned in the creation of LTNs.

@@

All weights are between 0 and 1, and the values in the \textit{Weighted} profile are chosen to be inversely proportional to the stress level experienced by cyclists on them. The \textit{Unweighted} weighting profile is used to compare increases in route length resulting from two different approaches:
